Online learning methods for financial time series forecasting

### 2017-11-18 slides/defense-slides.tex
Drunk and the dog example

\titlegraphic{
    \tikz[overlay,remember picture]
        \node[at=(current page.south east), anchor=south east] {
            \includegraphics[height=1.5cm]{img/DIT}
        };
}

@@

%\begin{frame}
%\frametitle{Outline}
%\begin{itemize}
%\item Motivation: economic relations
%\item Cointegration and Integration concepts
%\item VECM model
%\item Proposal
%\item Experiments
%\item Conclusions
%\end{itemize}
%\end{frame}

@@

\begin{frame}
\frametitle{Motivation}
\begin{itemize}
\item Financial time series are mainly non-stationary.  However, one or more linear
combinations of non-stationary time series can be stationary even though
individually they are not. When this happens it is said they have a long-run
equilibrium relationship and the variables are \textbf{cointegrated}.
\item The Vector Error correction model (VECM) is used to model cointegrated time series but is used only with batch data and rarely used with high frequency data.
\end{itemize}
\end{frame}

>>>>

\titlegraphic{
    \tikz[overlay,remember picture]
        \node[at=(current page.south), anchor=south] {
            \includegraphics[height=1.5cm]{img/DIT}
        };
}

@@

\begin{frame}
\frametitle{Outline}
\begin{itemize}
\item Motivation: economic relations
\item Cointegration and Integration concepts
\item VECM model
\item Proposal
\item Experiments
\item Conclusions
\end{itemize}
\end{frame}

@@

\begin{frame}[t,fragile]{Random walk and Cointegration Illustration}
 \begin{itemize}
  \item<1-> The drunkard's walk
  \item<2-> The dog's walk
  %\item<3-> The drunk and dog's walk
 \end{itemize}

\begin{columns}
\begin{column}{.4\linewidth}<1->
\begin{center}
        \begin{tikzpicture}[overlay]
            \node[yshift=-50] (img2) {\includegraphics[scale=1.4]{img/drunk}};
        \end{tikzpicture}
\end{center}
\end{column}
\begin{column}{.08\linewidth}<2->
        \begin{tikzpicture}[overlay]
            \node[yshift=-50] (img2) {\includegraphics[scale=0.06]{img/dog}};
        \end{tikzpicture}
\end{column}
%\begin{column}{.5\linewidth}<3->
%    \begin{center}
%        \begin{tikzpicture}[overlay]
%            \node[yshift=-50] (img2) {\includegraphics[scale=0.1]{img/mananddog}};
%        \end{tikzpicture}
%    \end{center}
%\end{column}
\end{columns}
\end{frame}

\begin{frame}[t,fragile]{Random walk and Cointegration Illustration}
 \begin{itemize}
  \item The drunk and dog's walk
 \end{itemize}
    \begin{center}
        \begin{tikzpicture}[overlay]
            \node[yshift=-60] (img2) {\includegraphics[scale=0.1]{img/mananddog}};
        \end{tikzpicture}
    \end{center}
\end{frame}

\begin{frame}
\frametitle{Motivation}

The relationship between non-stationary time series can be modelled if exists a linear combination of them that turns out to be stationary.
%Financial time series are mainly non-stationary.  However, one or more linear
%combinations of non-stationary time series can be stationary even though
%individually they are not. 
When this happens it is said they have a long-run
equilibrium relationship and the variables are {\color{red} cointegrated}.
\
% The Vector Error correction model (VECM) is used to model cointegrated time series but is used only with batch data and rarely used with high frequency data.
